### 2017-11-10 Cars/paper.tex
minor tweaks

Multiple groups of differing driver behaviour can be allowed while still retaining heterogeneity with each group by jointly estimating each vehicle driver's individual parameter vector, $\theta_i$, as part of a heirarchical model, independently drawing $\theta_i$ from a $K$ component mixture of multivariate normal distributions, augmenting each $\theta_i$ with a mixture component $k_i = 1, \dots, K$ such that 
\begin{equation}
\theta_i | k_i = j \sim N(\mu_j, \Sigma_j).
\end{equation}
For each $j = 1, \dots, K$, multivariate normal priors are chosen for $\mu_j$ with mean $\bar{\mu}_j$ and variance matrix $\Omega_j$, Inverse Wishart priors are chosen for $\Sigma_j$ with degrees of freedom $\tau_j$ and scale matrix $\Psi_j$, and finally $k_{i, j}$ has a Dirichlet prior with parameters $\alpha_{i, j} = \alpha_i$. This can be estimated with MCMC methods.

\section{Online Classification}

@@

Modelling process:
\begin{itemize}
\item Fit heirarchical model from section 3 for cars $i = 1, \dots N$ before car starts driving - eg. During manufacturing process so unlimited time available.
\item Observe a new car, say car $N + 1$.
\item Want to learn about parameters $\theta_{N+1}$ and which group $k_{N+1}$ the driver belongs to
\item $p(\theta_{N+1}, k_{N+1} | y_{1:N+1}) \propto p(y_{N+1, 1:T} | \theta_{N+1}) p(\theta_{N+1} | k_{N+1} \beta)p(k_{N+1}) p(\beta | y_{1:N})$
\item Essentially using mixture distribution posterior fit for cars 1 to N as prior for $\theta_{N+1}$.
\item However we want to be able to do this as we observe $y_{N+1}$, eg: Fit distribution to $p(\theta_{N+1}, k_{N+1} | y_{N+1, 1:10}, y_{1:N})$, then to $p(\theta_{N+1}, k_{N+1} | y_{N+1, 1:11}, y_{1:N})$ etc.
\item To do this in VB we need to make two further approximations:
\begin{enumerate}
\item Fit a parametric distribution to the MCMC posterior
\item Replace each  $p(\theta_{N+1} | y_{i, 1:S}, y_{1:N})$ used to fit $q(\theta_{N+1} | y_{N+1, 1:S+1})$ with the VB fit from the last step, $q(\theta_{N+1} | y_{N+1, 1:S})$.
\end{enumerate}
\end{itemize}

@@

>>>>

Multiple groups of differing driver behaviour can be allowed while still retaining heterogeneity with each group by jointly estimating each vehicle driver's individual parameter vector, $\theta_i$, as part of a heirarchical model, independently drawing $\theta_i$ from a $K$ component mixture of multivariate normal distributions, augmenting each $\theta_i$ with a mixture component $k_i = 1, \dots, K$ such that 
\begin{equation}
\theta_i | k_i = j \sim N(\mu_j, \Sigma_j).
\end{equation}
For each $j = 1, \dots, K$, multivariate normal priors are chosen for $\mu_j$ with mean $\bar{\mu}_j$ and variance matrix $\Omega_j$, Inverse Wishart priors are chosen for $\Sigma_j$ with degrees of freedom $\tau_j$ and scale matrix $\Psi_j$. $k_{i}$ has a multinomial distribution with mixture probabilities $\boldsymbol{\pi_i} = \{\pi_{1, i}, \dots, \pi_{K, i}\}$, where $\boldsymbol{\pi_i}$ has a Dirichlet prior with parameters $\alpha_1, \alpha_2, \dots, \alpha_K$. This can be estimated with MCMC methods.

\section{Online Process}

@@

Modelling process:
\begin{itemize}
\item From Section 3 we have the distribution $p(\beta | y_{1:N})$.
\item The posterior distribution of a new car is given by
\begin{equation}
p(\theta_{N+1} | y_{1:N+1}) \propto p(y_{N+1} | \theta_{N+1}) p(\theta_{N+1} | \beta) p (\beta | y_{1:N})
\end{equation}
\item As N is large we can replace $ p(\theta_{N+1} | \beta) p (\beta | y_{1:N})$ with $ p(\theta_{N+1} | \beta_{MAP})$ where $\beta_{MAP}$ is the maximum of $ p (\beta | y_{1:N})$, or some other suitable point estimate.
\item Observe $y_{N+1, 1:S_1}$, fit VB $q(\theta_{N+1} | y_{N+1, 1:S_1}) \approx p(\theta_{N+1} | y_{1:N}, y_{N+1, 1:S_1})$
\item Observe $y_{N+1, S_1+1:S_2}$, in this case the model becomes
\begin{equation}
p(\theta_{N+1} | y_{1:N}, y_{N+1, 1:S_2}) \propto p(y_{N+1, S_1+1:S_2} | \theta_{N+1})p(\theta_{N+1} |  y_{1:N}, y_{N+1, 1:S_1})
\end{equation}
\item Set $p(\theta_{N+1} |  y_{1:N}, y_{N+1, 1:S_1}) = q(\theta_{N+1} | y_{N+1, 1:S_1})$, fit VB  $q(\theta_{N+1} | y_{N+1, 1:S_2}) \approx p(\theta_{N+1} | y_{1:N}, y_{N+1, 1:S_2})$
\item Repeat as new data is observed
\end{itemize}

@@

Comparisions:
\begin{enumerate}
\item VB Approximation with the above process
\item One Car MCMC/VB without prior information
\item One Car MCMC/VB with mild prior informaiton - eg. One Component
\end{enumerate}
Compare performance with different observed samples - prior informaiton should be very beneficial for first few seconds but expect methods to converge over time.
